Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2022-03-08 papers/03 journal final/journal_v16.tex
g

%\paragraph*{constraint related to trading with main grid}
Finally, the power exchanged with the main grid must satisfy the following constraints:
\begin{subequations}
\begin{align}
	p^{\mathrm{tg}}_{y} &= 0, \quad \forall y \notin \mc B^{\mathrm{mg}}, \label{eq:grid_ex}\\
	\sigma^{\textrm{mg}}_h + b_h &= \sum_{y\in\mc B}p^{\mathrm{tg}}_{y,h}, \quad \forall h \in \mathcal H, \label{eq:grid_const2}
\end{align}
\end{subequations}
where \eqref{eq:grid_ex} is imposed by definition that the busses that are not directly connected with the main grid do not exchange  power with the main grid, whereas \eqref{eq:grid_const2} ensures that the power traded by the prosumers with the main grid (in the trading network) corresponds to the power exchanged between the whole distribution network and the main grid.

%\begin{definition}[Extended P2P market model]
%\label{def:p2p_ext}
\section{A Distributed Market-clearing Mechanism}
\label{sub:alg}
\subsection{Market-Clearing Game and Variational Equilibria}
By letting the physical variables of the distribution network be handled by a DNO (i.e., agent $N\!+\!1$), the P2P market clearing problem can be compactly written as the problem of finding the optimal strategy profiles $u_i^*$'s in \eqref{eq:locOpt}, for all $i \in \mc N^+$, where the decision variable $u_i$ is defined as
$$u_i \hspace{-2pt} = \hspace{-2pt}\begin{cases} \col\hspace{-2pt}\left(p_{i}^{\mathrm{di}},{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}, } p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)\hspace{-2pt}, \ \qquad \qquad \;  \forall  i \in \mc N,\\
	\col\hspace{-2pt}\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right)\hspace{-2pt},  \; \quad i\!=\! N\!+\!1;
		\end{cases}$$ 
the cost function is defined as
	\begin{multline}
	J_i(u_i,u_{-i}) =
f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) + f_{i}^{\mathrm{st}}({p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}})+ f_{i}^{\mathrm{tr}} \left( \{ p_{(i,j)}^{\mathrm{tr}} \}_{j \in \mc N_i} \right)\\
    + f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\sigma^{\textrm{mg}} \right), \quad \forall  i \in \mc N,
 \label{eq:cost_def}
	\end{multline}
whereas\footnote{Here, we assume that the DNO does not have preferences on the outcome, provided that it is a feasible solution for the network.} $J_{N+1}=0$; the local action set is
\begin{align}
\label{eq:constr_def}
\mc U_i =
\left\{
\begin{array}{l r}
\left\{u_i \,|~ \text{\eqref{eq:p_dg_bound}, \eqref{eq:x}, \eqref{eq:l_pow_b}, \eqref{eq:p_t_bound} hold} \, \right\}, & \forall i \in \mc N, \\
\left\{ u_i \,|~ \text{\eqref{eq:pf_pq},\eqref{eq:line}, \eqref{eq:grid_ex} hold} \,\right\}, & i\!=\!N\!+\!1;
\end{array}
\right.
\end{align}
and finally, the set of coupling constraints is 
\begin{equation}
\label{eq:Cconstr_def}
\mc C = \left\{
u~|~ \text{\eqref{eq:rep_const}, \eqref{eq:p_mg_bound}, \eqref{eq:p_bal_p}, \eqref{eq:grid_const2} hold}
\right\}.
\end{equation}

\begin{remark}
Our definitions of $J_i$, $\mc U_i$, $\mc C$ satisfy Assumption~\ref{as:gen}. Moreover, these definitions can be expanded by incorporating additional cost terms, for example, related to the degradation of storage units and constraints (e.g. ramping constraints of dispatchable generation units), as long as Assumption \ref{as:gen} remains satisfied.  {Additionally, instead of linear power flow equations in \eqref{eq:pf_all}, a nonlinear convex relaxation, such as a second order cone or semi-definite programming as discussed in \cite[Sect. II-A]{molzahn2017} can be considered since it still satisfies Assumption 1. In this case, only the definition of $\mc U_{N+1}$ differs from the current formulation.}\eod
\end{remark}

@@

\textsc{Algorithm 2}. Prosumer $i$'s local update

@@

\medskip
\noindent 
(i) \text{Primal update (network physical variables):}\\[.2em]
\hspace*{.15em}
$\left\lfloor
\begin{array}{l}
\psi(k) = \col \left( 
	\left\{
	\0,\mu^{\text{tg}}(k) + \mu_y^{\text{pb}}(k), 
	\{ \mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
	\right\}_{y \in \mc B} \right)\\[.7em]
%
u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) + (\alpha_{N+1})^{-1} \psi(k) \right)
\vspace*{.1em}
\end{array}
\right.
$

>>>>

%\paragraph*{constraint related to trading with main grid}
Finally, the power exchanged with the main grid must satisfy the following constraints:
\begin{subequations}
\begin{align}
	p^{\mathrm{tg}}_{y} &= 0,  &\forall y \notin \mc B^{\mathrm{mg}}, \label{eq:grid_ex}\\
	\sigma^{\textrm{mg}}_h + b_h &= \sum_{y\in\mc B}p^{\mathrm{tg}}_{y,h},  &\forall h \in \mathcal H, \label{eq:grid_const2}
\end{align}
\end{subequations}
where \eqref{eq:grid_ex} is imposed by definition that the busses that are not directly connected with the main grid do not exchange  power with the main grid, whereas \eqref{eq:grid_const2} ensures that the power traded by the prosumers with the main grid (in the trading network) corresponds to the power exchanged between the whole distribution network and the main grid.

%\begin{definition}[Extended P2P market model]
%\label{def:p2p_ext}
\section{A Distributed Market-clearing Mechanism}
\label{sub:alg}
\subsection{Market-Clearing Game and Variational Equilibria}
By letting the physical variables of the distribution network be handled by a DNO (i.e., agent $N\!+\!1$), the P2P market clearing problem can be compactly written as the problem of finding the optimal strategy profiles $u_i^*$'s in \eqref{eq:locOpt}, for all $i \in \mc N^+$, where the decision variable $u_i$ is defined as
$$u_i \hspace{-2pt} = \hspace{-2pt}\begin{cases} \col\hspace{-2pt}\left(p_{i}^{\mathrm{di}},{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}, } p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)\hspace{-2pt}, \ \qquad \qquad \;  \forall  i \in \mc N,\\
	\col\hspace{-2pt}\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right)\hspace{-2pt},  \; \quad i\!=\! N\!+\!1;
		\end{cases}$$ 
the cost function is defined as
	\begin{multline}
	J_i(u_i,u_{-i}) =
f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) + f_{i}^{\mathrm{st}}({p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}})+ f_{i}^{\mathrm{tr}} \left( \{ p_{(i,j)}^{\mathrm{tr}} \}_{j \in \mc N_i} \right)\\
    + f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\sigma^{\textrm{mg}} \right), \quad \forall  i \in \mc N,
 \label{eq:cost_def}
	\end{multline}
whereas\footnote{Here, we assume that the DNO does not have preferences on the outcome, provided that it is a feasible solution for the grid.} $J_{N+1}=0$; the local action set is
\begin{align}
\label{eq:constr_def}
\mc U_i =
\left\{
\begin{array}{l r}
\left\{u_i \,|~ \text{\eqref{eq:p_dg_bound}, \eqref{eq:x}, \eqref{eq:l_pow_b}, \eqref{eq:p_t_bound} hold} \, \right\}, & \forall i \in \mc N, \\
\left\{ u_i \,|~ \text{\eqref{eq:pf_pq},\eqref{eq:line}, \eqref{eq:grid_ex} hold} \,\right\}, & i\!=\!N\!+\!1;
\end{array}
\right.
\end{align}
and finally, the set of coupling constraints is 
\begin{equation}
\label{eq:Cconstr_def}
\mc C = \left\{
u~|~ \text{\eqref{eq:rep_const}, \eqref{eq:p_mg_bound}, \eqref{eq:p_bal_p}, \eqref{eq:grid_const2} hold}
\right\}.
\end{equation}

\begin{remark}
The definitions of $J_i$, $\mc U_i$, $\mc C$ in \eqref{eq:cost_def}, \eqref{eq:constr_def}, \eqref{eq:Cconstr_def} satisfy Assumption~\ref{as:gen}. Moreover, these definitions can be expanded by incorporating additional cost terms, for example, related to the degradation of storage units and constraints (e.g. ramping constraints of dispatchable generation units), as long as Assumption \ref{as:gen} remains satisfied.  {Additionally, instead of linear power flow equations in \eqref{eq:pf_all}, a nonlinear convex relaxation, such as a second order cone or semi-definite programming as discussed in \cite[Sect. II-A]{molzahn2017} can be considered since it still satisfies Assumption 1. In this case, only the definition of $\mc U_{N+1}$ differs from the current formulation.}\eod
\end{remark}

@@

\textsc{Algorithm 2}. Local update of Prosumer $i$

@@

\medskip
\noindent 
(i) \text{Primal update (grid physical variables):}\\[.2em]
\hspace*{.15em}
$\left\lfloor
\begin{array}{l}
\psi(k) = \col \left( 
	\left\{
	\0,\mu^{\text{tg}}(k) + \mu_y^{\text{pb}}(k), 
	\{ \mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
	\right\}_{y \in \mc B} \right)\\[.7em]
%
u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) + (\alpha_{N+1})^{-1} \psi(k) \right)
\vspace*{.1em}
\end{array}
\right.
$
